The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to paper

If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.  The monomials and the simple normal crossing cases are computed as the reciprocal of maximal exponent of the factors.
Outside of that simple case, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf. \cite{ShibutaTakagiLCThresholds}).

@@

o10 = true
\end{MyVerbatim}
}
\medspace
There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).  Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.  We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.  We also verify that these subsets generate ideals of the correct height.  Note, this calls {\tt factor f}, which may be slow.  The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.

This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.  Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).

>>>>

If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf. \cite{ShibutaTakagiLCThresholds}).

@@

o10 = true
\end{MyVerbatim}
}
\medspace
